Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
Typo

Termination for bit-vector programs is known to be
PSPACE-complete~\cite{DBLP:conf/tacas/CookKRW10}.  We first record the
expected results for soundness and completeness of our algorithm for
deciding it.  Our strategy for proving soundness and completeness
is first to prove that Algorithm~\ref{alg:cegis} (as instanciated
with \newC as a background logic) is a semi-decision
procedure.  Next, we will show that $\mathcal{L}$ is expressive enough
to compute (non-)termination proofs for every bit-vector program.
We will then combine these results to show that the procedure as a whole
terminates with a valid proof for every input program.
%
\begin{theorem}\label{thm:synth-sound}
Algorithm~\ref{alg:cegis} is sound -- if it terminates with witness $(P, x_0)$, then
$(P, x_0) \models \sigma$.
\end{theorem}

@@

\begin{corollary}
\label{cor:cegis-newc}
 Since safety of \newC programs is decidable, Algorithm~\ref{alg:cegis} is semi-complete
 when instanciated with \newC as a background theory.
\end{corollary}

@@

>>>>

Termination for bit-vector programs is known to be
PSPACE-complete~\cite{DBLP:conf/tacas/CookKRW10}.  We first record the
expected results for soundness and completeness of our algorithm for
deciding it.  Our strategy for proving soundness and completeness
is first to prove that Algorithm~\ref{alg:cegis} (as instantiated
with \newC as a background logic) is a semi-decision
procedure.  Next, we will show that $\mathcal{L}$ is expressive enough
to compute (non-)termination proofs for every bit-vector program.
We will then combine these results to show that the procedure as a whole
terminates with a valid proof for every input program.
%
\begin{theorem}\label{thm:synth-sound}
Algorithm~\ref{alg:cegis} is sound -- if it terminates with witness $(P, x_0)$, then
$(P, x_0) \models \sigma$.
\end{theorem}

@@

\begin{corollary}
\label{cor:cegis-newc}
 Since safety of \newC programs is decidable, Algorithm~\ref{alg:cegis} is semi-complete
 when instantiated with \newC as a background theory.
\end{corollary}

@@

\nocite{fisher2009phylogeny}
